% style to be determined
\documentclass[a4paper]{article}

% The file lwa.sty is the style file for LWA.
\usepackage{lwa}

% Use the postscript times font!
\usepackage{times}
\usepackage{latexsym}

%
\usepackage{makeidx}  % allows for indexgeneration
\usepackage{graphicx}  % allows for indexgeneration
\usepackage{amsmath, amssymb}
%\usepackage{subfigure}

%\usepackage{pstricks}
%\usepackage{epic}
%\usepackage{eepic}
%\usepackage{fmtcount}
%\usepackage{multirow}

\makeindex
%

\begin{document}

\newcommand{\argmax}{\text{arg max}}
\newcommand{\avg}{\text{avg}}



% first contribution
\title{Mining Music Playlog Files to Recommend Next Songs}
%\title{What to listen to next?}
%
%\titlerunning{Hamiltonian Mechanics}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Andre Busche, Artus Krohn-Grimberghe, Lars Schmidt-Thieme \\
University of Hildesheim, Germany\\
\{busche, artus, schmidt-thieme\}@ismll.uni-hildesheim.de}

%
%
%%%% list of authors for the TOC (use if author list has to be modified)

\index{Busche, Andre}
\index{Krohn-Grimberghe, Artus}
\index{Schmidt-Thieme, Lars}

% use the command \index{<name>} for index entries

\maketitle              

\setcounter{footnote}{0}

\begin{abstract} 

This paper presents a collaborative approach to music playlist recommendation in a large scale scenario.
We show that a simple markov-chain based algorithm improves performance compared to baseline models when neither content, nor user metadata is available.	


\end{abstract} 

\input{sec1}

\input{sec2}

\input{sec3}

\input{sec4}

\input{sec5}


\begin{thebibliography}{1}


\bibitem{ragno05}
R. Ragno, CJC Burges, C. Herley:
Inferring similarity between music objects with application to playlist generation,
Proceedings of the 7th ACM SIGMM international workshop on Multimedia information retrieval,
pp. 73-80.

\bibitem{flexer08}
Flexer, A., et al.: 
Playlist Generation Using Start and End Songs, 
ISMIR 2008,
pp. 173-178

\bibitem{maillet09} % has used tags
Maillet, F., et al.:
Steerable Playlist Generation by Learning Song Similarity from Radio Station Playlists,
ISMIR 2009,
pp. 345-350

% evtl: 
\bibitem{sordo08}
The Quest for Musical Genres: Do the Experts and the Wisdom of the Crowds Agree?,
ISMIR 2008,
pp. 255-260


% evtl. for tags:
% \bibitem{christine09}
% Leandro Balby Marinho, Christine Preisach, Lars Schmidt-Thieme (2009):
% Relational Classification for Personalized Tag Recommendation, 
% (ECML/PKDD-DC 2009), 
% Bled, Slovenia

\bibitem{turnbull08}
Turnbull, D., Barrington, L., Lanckriet, G.:
Five Approaches to Collecting Tags for Music,
ISMIR 2008,
pp. 225-230

\bibitem{casey08}
Casey, M. A., et al.:
Content-Based Music Information Retrieval: Current directions and Future Challenges,
Proceedings of the IEEE, Vol 96, No. 4, April 2008,
pp. 668-696





\end{thebibliography} 


\end{document}
